%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% $Id: inhalt.tex 112 2015-10-06 14:31:36Z klugeflo $
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Remarks on the Content}
\label{c:content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Scope of the thesis:
  \begin{description}
  \item[Bachelor thesis] 25-35 pages
  \item[Master thesis] 50-60 pages
  \end{description}
  Pure text only, all indices, title pages etc. not included.
  These figures are only rough guidance values, depending on the topic, it is possible to deviate from these values.
  It is therefore essential that you discuss the actual length target with your supervisor!
  Keep in mind that writing short, \textbf{concise}, yet \textbf{comprehensive} is harder and more valuable than producing a lot of text with repetitions.
\item Be sure to consider \cite{keshav07ccr} for your literature research.
\item Your final thesis is a scientific work that must also meet appropriate quality requirements.
  \begin{itemize}
  \item Do not use colloquial terms.
  \item Be sure to back up any statements you make with
    appropriate arguments or literature references.
  \item Perform a spell check before submitting.
    A good tool for this is for example
    \texttt{aspell}, which is also provided for use in editors such as Emacs
    is also intended for use.
  \end{itemize}
  \item This book \cite*{glasman2009science} is another great resource for improving your writing style in English, in particular for non-native speakers of English.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: thesis
%%% TeX-PDF-mode: t
%%% End: 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%<!-- Local IspellDict: en -->
